%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LaTeX template for reading report
% Author: Shuo Yang
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,epsfig,graphics,hyperref,amsthm,mathtools,enumitem}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\hypersetup{colorlinks=true}

\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.575in}
\setlength{\textheight}{9.25in}
\setlength{\oddsidemargin}{-.25in}
\setlength{\evensidemargin}{-.25in}

\reversemarginpar
\setlength{\marginparsep}{-15mm}

\newcommand{\rmv}[1]{}
\newcommand{\bemph}[1]{{\bfseries\itshape#1}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\imply}{\to}
\newcommand{\bic}{\leftrightarrow}

% Some user defined strings for the homework assignment
%
\def\CourseCode{CS525}
\def\ReportNo{4}
\def\Category{Reading Report}
\def\PaperTitle{Delayed Internet Routing Convergence}
\def\Author{Shuo Yang}

\begin{document}

\noindent

\CourseCode \hfill \Category

\begin{center}
Reading Report \#\ReportNo\\
Paper: \PaperTitle\\
Student: \Author\\
\end{center}

% A horizontal split line
\hrule\smallskip
\vspace{1.5em}

The paper's strength lies in their experimental instrumentation of key
portions of the Internet without solely relying on simulation results, 
and the BGP convergence behaviors they observed based on the 2-year
long data collection. The experiment results are convincing, but their
analysis is not that convincing when they tried to justify their
observations. 

\vspace{0.5em}
They adopted an oversimplified BGP convergence model for analysis. For
example, modeling each AS as a single node, choosing a full mesh
network topology, unbounded delay and treating a BGP processing as a
single linear, global queue, etc. These assumptions do not reflect the
reality of the Internet, thus cannot be used as a good indicator for
BGP convergence. They spent lots of time talking about upper bound and
lower bound on convergence. But both of these bounds are unlikely to
occur in practice. Unfortunately, they further analyzed the results
based on this oversimplified model to back up their previous mentioned
results. It gives me the feeling that their analysis does not make
the results more convincing, though intuitively, these results do make
sense.

\vspace{0.5em}
In general, the model and analysis appears in such a way that they
seems to be used to deliberately justify the experiment results and
observations.

\vspace{0.5em}
I would argue that trying to build an analytical model for BGP
convergence may not be feasible due to the complex nature of the
Internet thus should not be used to back up the experiment
results. Rather, we need to shift our focus to the data itself. The
date set collected during 
the 2-year's experiment is a valuable resource which are worthy of
exploring since they are real Internet inter-domain routing
data. Unlike simplified BGP convergence model, these data cannot lie
and should reflect the reality of the Internet. Thus it matters how we
are going to use and interpret the data. The simple
exploratory data analysis combined with some basic data visualization
techniques might be the first step for us to get some insights into why
Internet behaves in such way. The more-in-depth and complicated data
analysis with advanced data visualization can be applied to follow
up.

\vspace{0.5em}
I also noticed that the paper always
present figures with a subset of data and a cutoff scale for clarity
purpose. They also mentioned correlation between observations in a
couple of places in the paper without using large amount of data and
visualization to 
backup this correlation. These might be a sign that they did not do
many in-depth data analysis and visualization, which is something they
could have done for improvement and more sound results.

\vspace{0.5em}
Overall, the paper is strong in its first part (section 1,2,3 and 4),
but weak in second part (section 5 and 6). It is a good engineering
practice to measure the Internet BGP convergence behavior along with
their sharp observations, but it is lack of mature theoretical and
analysis support.

\end{document}
